\cleardoublepage
\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
	First and foremost, I would like to thank Prof. Dr. Gustavo Alonso and Dr. Ghislain Fourny for giving me an opportunity to work with them. Their expertise is undeniable, and it is always a special kind of honor working together with people like them. More importantly, I want to thank them for showing empathy and feelings. Gustavo Alonso was the person that guided me through my first semester at ETH. The first-semester depression is something every non-bachelor ETH graduate goes through, every single one. Not a single person at ETH could help me. I felt alone and abandoned. Gustavo is the only one that took his time to truly hear me out, and he gave me worthy advice. I thank Ghislain for being by far one of the best lecturers I have ever seen. The passion I saw for his work is remarkable. It inspired me and restored faith that a person can truly enjoy and love their work. In addition, I thank Michael Kay for being very reactive and helpful and consulting us regarding Saxon.
	
	I am a very grateful person today, but I was not always like that. I took many things for granted, and for you to understand the list of people I am grateful to, you should know my story. 
	
	I was born 27 years ago in a war-devastated country. Yes, I remember my dad jumping over me and protecting me with his body thinking that the house would collapse when a tomahawk hit a nearby military base. People screaming and running in a panic over each other to hide in the basement. Skies being so orange at night, it seemed like a never-ending sunset. Yes, I remember being bullied and mistreated by other kids in primary school. Being laughed at for anything, even things that were not even true. Injustice and incapability of the system to protect me. Alone, I promised myself I would never be weak again. I had to grow up. Yes, I remember setting an example for everyone. Obtaining numerous awards and recognitions. Finally graduating as the single best MSc student of the entire generation. Yes, I remember leaving the life I was building for 25 years. Coming to Switzerland as an already defined person, pursuing the dream of ETH and a better future for my family, leaving people back home in tears. Quitting my stable job, risking it all with 0 income or support, eating refills of lunch in Polymensa for dinner. Again being mistreated, by flatmate. Being discriminated because of my country of origin. Even though I was not spoiled and I was used to defeat, I cried every day, broken, hopeless, depressed. I was going to sleep while praying not to wake up the next morning. Yes, I remember the generosity and a hand of salvation. Building new friendships, engaging in team projects. Getting a 70\% workload job while maintaining my studies. Finally being able to bring my wife to Switzerland. Yes, I remember my cheating ex-wife leaving me for a rich Swiss boy. Losing my purpose, empty on the inside. Even with the same shell with a fake smile on the outside, people could not recognize me anymore. Not being able to pick up the threads of my old life, time passed, things were not the same. Failed to build a new life, just wandering around like a lost undefined soul. Yes, I remember losing my dad. He survived an aneurysm with less than 1\% chances. He did not survive me leaving. Grief over me killed him.
	
	I am not writing this so that you can pity me. I am writing to share the story of how I learned to be grateful.
	
	If you are thinking of quitting, do not do it. If you believe your life is miserable, it is not. Stop for a moment and look back at your life. Always look back at what you already have. Look at all the privileges you are entitled to, but you are taking them for granted. You came to this world as a tabula rasa, and the world owes you nothing by childbirth. Whatever you already have in life, you should consider a blessing. If life taught me anything: In a blink of an eye, you could lose everything. 
	
	In the end, it does not matter what you will achieve. What matters is what kind of life you are going to live. Live every day like it is your last and you will see how simple life is. And if you wake up one day, hating your life and the avatar that you have become, gather strength to reset and start all over again. To everyone that did terrible things to me, I can only say thank you. Thank you for making me play a game called life in veteran mode. You made me stronger. You made me what I am today. I died and I was reborn more than ten times. What is your excuse? 
	
	The list of people I am grateful to is endless, but I am limited to 2 pages. Whoever is left out should know that they still have a place in my heart: 
	
	\begin{itemize}
		\item Nikola and Ivana - my brother and my mom, for being the only two people in the world for whom I would give my life
		\item Dusan Malinov - for implanting the idea of ETH in the first place
		\item Team 7 GameLab - for healing me after first-semester depression
		\item Daniel Keller - my boss at ABB who believed in my skills and capabilities when even I did not believe in them
		\item Simon Weber - for pulling out more in me and not slowing me down
		\item Ex-wife - for teaching me what being manipulated actually means
		\item Ex-flatmate - for showing me how a toxic person can break a family
		\item Tommaso Ciussani - for saving me from abusive flatmate by sharing his room with me until I found a better place to live
		\item Costanza Importa - my teammate in CIL project for being human, having empathy and covering up for me when I lost my dad
		\item Regula Cinelli - for teaching me not to wait for time to pass in order to get something over with, but to picture yourself as a winner
		\item Svilen Stefanov - for being a true friend and my consigliere that I perhaps do not deserve
		\item Team Nignite - for heartwarming working environment and support
		\item Diana Ghinea - for seeing the value in me when I could not, for waking up desire and fire in me to be a better version of myself
		\item My dad Milutin - for telling the same stories ten and more times over and over again, teaching me that life is about memories
	\end{itemize}
	
\end{abstract}