
\chapter{Introduction}
\label{chapter:introduction}
The increasing amount of data available to process, as well as the ever-growing discrepancy between storage capacity, throughput and latency, has forced the database community to come up with new querying paradigms in the last two decades. Data became nested and heterogeneous (JSON), and is increasingly processed in parallel (Spark). In order to make querying more efficient and accessible, Rumble \cite{RumblePaper} is an engine that automatically runs queries on semi-structured and unstructured documents on top of Spark, using the JSONiq language. 

JSONiq \cite{JSONIQORG} is a functional and declarative language that addresses these problems with its most useful FLWOR expression, which is the more flexible counterpart of SQL’s SELECT FROM WHERE. It inherits 95\% of its features from XQuery, a W3C standard.

The XQuery/XPath 3.* Test Suite (QT3TS) \cite{TestSuite} provides a set of tests with over 30000 test cases designed to demonstrate the interoperability of W3C XML Query Language, version 3.0 and W3C XML Path Language implementations.

The high-level idea of this work is to implement a Test Driver that can directly use QT3TS in order to test and verify Rumble's implementation. The implementation of the Test Driver has been carried out gradually through iterations. We have analyzed the output of each iteration to measure the implementation success. Test Driver and its architecture have gradually evolved and improved through several phases of implementation. In parallel to Test Driver, we have helped improve Rumble implementation by filing bug reports. We have also designed strategies to automatically convert non-JSONiq test cases to JSONiq that led to implementing a Test Converter for the XQuery to JSONiq conversion.